Codebook created on 2024-01-02 at 2024-01-02 11:37:22.192211

### 2024-01-02 Data/AnalysisData/codebook_plot_46_data_REV.Rmd
Opened up the Many Labs retrieved data for the project.

---
title: "Codebook created on 2023-11-13 at 2023-11-13 11:23:30.376704"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_Plot_46_data.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2024-01-02 at 2024-01-02 11:37:22.192211"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_plot_46_data_rev.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```
